Issues with Dynamical Measurements Across the Disk

### 2019-02-15 paper/ms.tex
Fix minor formatting things

\subsection{The effect of midplane determination on orbit and action
calculations} \label{ssec:cartoon} We present a cartoon in
Figure~\ref{fig:cartoon} to show how an inaccurate determination of the
midplane leads to a phase-dependence of the actions calculated from an orbit
specified by a phase-space point and an assumed potential model. The y-axis
corresponds to the vertical height of the orbit and the x-axis orbital phase.
The solid gray line indicates the ``true'' orbit of the star; that is, its
orbit as it oscillates around the true midplane. The dashed gray line is an
erroneous midplane assigned to the potential model which an observer uses to
integrate the orbit of the star and hence estimate its actions. The model
potential is otherwise identical to the one in which the star is actually
moving.

@@

\begin{figure*}
\plotone{fig/cartoon.pdf}
\caption{Cartoon showing the effect an error in the determination of the
coordinate midplane can have on orbit integration and action estimation. The
x-axis shows the orbital phase and the y-axis the vertical height. The top
gray curve depicts an example ``true'' orbit oscillating about the true
midplane (horizontal solid gray line). Consider an observer who erroneously
assumes the midplane is located at the horizontal dashed line. Suppose this
observer measures the phase-space position of the star at two different
orbital phases (blue and pink points). If the observer were then to integrate
the star's orbit using a model potential with the erroneous midplane, they
would obtain the blue and pink curves for the star's orbit, respectively. The
actions estimated from these two  erroneous orbits would subsequently differ,
both from each other and from the actions estimated for the true orbit (in the
potential with the correct midplane). Hence an incorrect midplane in the
potential model assumed will induce phase-dependence in the actions estimated
for a given star in that potential.}
\label{fig:cartoon}
\end{figure*}

@@

We now repeat the same procedure for systematic offsets between 0 and 500 pc
in the $z$ and $x$ components. In Figure~\ref{fig:many_orbit_wrong_ref}, we
report the 95\uth minus 5\uth percentile divided by the true action value for
the three different fiducial orbits in Table \ref{tab:orbits}. The thick-disk
(\thickcolor) orbit is the one from Figure~\ref{fig:one_orbit_wrong_ref}, but
we also now consider the effect on the action determined for the thin-disk
(\thincolor) and halo (\halocolor) orbits.

>>>>

\subsection{The effect of midplane determination on orbit and action
calculations} \label{ssec:cartoon} We present a cartoon in
Figure~\ref{fig:cartoon} to show how an inaccurate determination of the
midplane leads to a phase-dependence of the actions calculated from an orbit
specified by a phase-space point and an assumed potential model. The $y$-axis
corresponds to the vertical height of the orbit and the $x$-axis orbital
phase. The solid gray line indicates the ``true'' orbit of the star; that is,
its orbit as it oscillates around the true midplane. The dashed gray line is
an erroneous midplane assigned to the potential model which an observer uses
to integrate the orbit of the star and hence estimate its actions. The model
potential is otherwise identical to the one in which the star is actually
moving.

@@

\begin{figure*}
\plotone{fig/cartoon.pdf}
\caption{Cartoon showing the effect an error in the determination of the
coordinate midplane can have on orbit integration and action estimation. The
$x$-axis shows the orbital phase and the $y$-axis the vertical height. The top
gray curve depicts an example ``true'' orbit oscillating about the true
midplane (horizontal solid gray line). Consider an observer who erroneously
assumes the midplane is located at the horizontal dashed line. Suppose this
observer measures the phase-space position of the star at two different
orbital phases (blue and pink points). If the observer were then to integrate
the star's orbit using a model potential with the erroneous midplane, they
would obtain the blue and pink curves for the star's orbit, respectively. The
actions estimated from these two  erroneous orbits would subsequently differ,
both from each other and from the actions estimated for the true orbit (in the
potential with the correct midplane). Hence an incorrect midplane in the
potential model assumed will induce phase-dependence in the actions estimated
for a given star in that potential.}
\label{fig:cartoon}
\end{figure*}

@@

We now repeat the same procedure for systematic offsets between $0$ and
$500\,\pc$ in the $z$ and $x$ components. In
Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth minus 5\uth
percentile divided by the true action value for the three different fiducial
orbits in Table \ref{tab:orbits}. The thick-disk (\thickcolor) orbit is the
one from Figure~\ref{fig:one_orbit_wrong_ref}, but we also now consider the
effect on the action determined for the thin-disk (\thincolor) and halo
(\halocolor) orbits.
